X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt}

### 2013-09-06 hedpc_natphys.tex
Marcos abstract, removed useless folders

%% ----------------------------------------------------------------------------------------------------------------
\begin{abstract}
    X-ray grating interferometry is a promising imaging technique sensitive to phase
    shifts, attenuation and scattering of the radiation.
    Applications of this technique in the diagnostically relevant energy range between $80$ and
    $\SI{150}{\kilo\electronvolt}$ are still largely unexplored due
    to the severe technical challenges.
    A phase-contrast technique at such high energies is of scientific and
    industrial interest for the analysis of materials of high atomic number or thickness
    as well as medical imaging.
    Here we show the design and operation of a Talbot-Lau
    interferometer with a target energy of $\SI{100}{\kilo\electronvolt}$ on
    a conventional X-ray tube and a compact geometry, with a total length of
    \SI{54}{\centi\metre}.
    The design features edge-on illumination in order to overcome the
    current limitations in the manufacturing of the gratings, and curved
    structures that match the beam divergence in order to allow for a large
    field of view and a short setup.
\end{abstract}

\maketitle

@@

Our design introduces the edge-on
illumination of circularly aligned structures. Edge-on illumination
(figure~\ref{Fig:schematic}), as
opposed to face-on illumination, exploits the dimension along the grating
lines to form a high aspect ratio of the structures in direction of the beam. The
effective structure height of the grating is then determined by the grating
dimension along the grating lines, which essentially allows arbitrarily high
aspect ratios. 
\begin{figure}[ht]
    \includegraphics[width=.5\textwidth]{figures/figure1.eps}
    \caption{Schematic of a grating
        interferometer for X-ray energies between 60 and
        \SI{150}{\kilo\electronvolt} in edge-on illumination mode. The
        aspect ratio is defined by the ratio of the travelling distance along the
        grating lines and the period and can be arbitrarily long. In order to avoid
        a reduction of the field of view, the grating structures are aligned on an
    arc.}
    \label{Fig:schematic}
\end{figure}

>>>>

%% ----------------------------------------------------------------------------------------------------------------
\begin{abstract}
    X-ray grating interferometry is a promising imaging technique sensitive
    to attenuation, refraction and scattering of the radiation. Applications
    of this technique in the energy range between $80$ and
    $\SI{150}{\kilo\electronvolt}$ are still largely unexplored due to the
    severe technical challenges. Phase-contrast X-ray imaging at such high
    energies is of relevant scientific and industrial interest, in
    particular for the investigation of materials with high atomic number or
    thickness as well as for medical imaging. Here we show the successful
    implementation of a Talbot-Lau interferometer operated at
    $\SI{100}{\kilo\electronvolt}$ using a conventional X-ray tube and a
    compact geometry, with a total length of $\SI{54}{\centi\metre}$. We
    suggest edge-on illumination of the gratings to overcome their current
    fabrication limits as well as curved structures, to match beam
    divergence and allow large field of views on a short and efficient
    setup.
\end{abstract}
\maketitle

@@

Our design introduces the edge-on
illumination of circularly aligned structures. Edge-on illumination
(figure~\ref{Fig:schematic}), as
opposed to face-on illumination, exploits the dimension along the grating
lines to form a high aspect ratio of the structures in direction of the beam. The
effective structure height of the grating is then determined by the grating
dimension along the grating lines, which essentially allows arbitrarily high
aspect ratios. 
\begin{figure}[ht]
    \includegraphics[width=.7\textwidth]{figures/figure1.eps}
    \caption{Schematic of a grating
        interferometer for X-ray energies between 60 and
        \SI{150}{\kilo\electronvolt} in edge-on illumination mode. The
        aspect ratio is defined by the ratio of the travelling distance along the
        grating lines and the period and can be arbitrarily long. In order to avoid
        a reduction of the field of view, the grating structures are aligned on an
    arc.}
    \label{Fig:schematic}
\end{figure}
